The hydra and the rooster

### 2020-08-24 latex/chapter-schutte.tex
proof simplification in L_alpha
corrections index

@@

The second and third axioms say that a subset $X$ of $\mathbb{O}$ is
(strictly) bounded if and only if it is countable. We use Florian Hatat's library on countable sets, written as he was a student of  \emph{\'Ecole Normale Supérieure de Lyon}.

@@

\begin{remark}
Please look at remark~\vref{warning:coercions}.
\end{remark}

@@

>>>>

We use Florian Hatat's library on countable sets, written as he was a student of  \emph{\'Ecole Normale Supérieure de Lyon}. A set $A$ is countable if there is an injective function from $A$ to $\mathbb{N}$ (see 
Library \href{../src/html/hydras.Schutte.Countable.html}%
{\texttt{Schutte.Countable}}).

\vspace{6pt}

@@

The second and third axioms say that a subset $X$ of $\mathbb{O}$ is
(strictly) bounded if and only if it is countable.

@@

% \begin{remark}
% Please look at remark~\vref{warning:coercions}.
% \end{remark}

@@

\index{Projects}
\begin{project}
There is no construction of ordinal multiplication in~\cite{schutte}. 
It would be interesting to derive this operation from Schütte's axioms,
and prove its consistence with multiplication in ordinal notations for 
$\epsilon_0$ and $\Gamma_0$.
\end{project}
